---
title: "Untitled"
output: html_document
date: '2023-05-18'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=9, message = FALSE, warning=FALSE, fig.retina = 2)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringi)
library(pander)
library(janitor)
library(scales)
library(magrittr)
library(viridis)
library(patchwork)
library(DT)
library(sf)
library(plotly)
library(flextable)
library(ggrepel)
library(magrittr)
library(readxlsb)
library(tidymodels)
library(widyr)
library(tidytext)
library(treemapify)
library(mdepriv)

theme_set(theme_light())

# disabling scientific notation
options(scipen = 100)

# pander tables all in one row
panderOptions('table.split.table', Inf)

# pander thousands separator
panderOptions("big.mark", ",")

# replace 
opts <- options(knitr.kable.NA = "")

`%out%` <- Negate(`%in%`)

# function for transposing df
transpose_df <- function(df) {
  t_df <- data.table::transpose(df)
  colnames(t_df) <- rownames(df)
  rownames(t_df) <- colnames(df)
  t_df <- t_df %>%
    tibble::rownames_to_column(.data = .) %>%
    tibble::as_tibble(.)
  return(t_df)
}

# scaling functions 
range01 <- function(x){(x-min(x))/(max(x)-min(x))}
range_wna <- function(x){(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))}

#mode function 
mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

```

```{r data}
pcode3_shape <- 
  sf::st_read("./data/syr_admbnda_uncs_unocha_20201217/syr_admbnda_adm3_uncs_unocha_20201217.shp", 
          quiet = TRUE)

nw_pcode3 <- read_excel("./data/2023HNO_PiN_Severity_detailedAoI_FORSHARE 15032023.xlsx", skip = 1, 
                  sheet = 1) %>%
  clean_names() %>% 
  filter(ao_c == "NW") %>% 
  pull(admin3pcode)

locations <- read_excel("./data/Locations.xlsx") %>% 
  clean_names()

pop <- read_excel("./data/Population_Data_May_2022_final_01122022_with_SADD.xlsx", 
           sheet = 5, 
           skip = 2) %>% 
  clean_names() %>% 
  select(admin0name_en:longitude_x, 
         final_est_of_id_ps_may_2022:family_avg_size_total_pop) %>% 
  rename(idps = final_est_of_id_ps_may_2022, 
         total_pop = final_est_of_total_pop_may_2022, 
         avg_family_size = family_avg_size_total_pop) %>% 
  filter(admin3pcode %in% nw_pcode3)

names_eq <- c(
  "date",
  "governorate",
  "district",
  "sub_district",
  "community",
  "admin4pcode",
  "casualties",
  "injuries",
  "completely_destroyed_houses",
  "damaged_unihabitable_houses",
  "temporary_accommodation_centres",
  "idps_in_all_centres",
  "schools_as_accomodation_centres",
  "idps_in_schools",
  "tents_needed",
  "blankets_mattresses_needed",
  "temporary_accommodation_centres_available", 
  "accessible_civil_defense",
  "latrines_available",
  "meals_needed_per_day",
  "need_blood_donations",
  "health_services_available",
  "necessary_medical_equipment",
  "rubble_volunteers",
  "telecoms_available",
  "electricity_available", 
  "heating_fuel_needed"
)

eq <- read_excel("./data/syria-earthquake-impact-20-march-2023.xlsx",
                 sheet = "DATASET") %>% 
  setNames(names_eq) %>% 
  left_join(pop %>% 
              select(admin4pcode, total_pop), 
            by = "admin4pcode") %>% 
  mutate(wounded_dead = casualties + injuries,
             damaged_houses = completely_destroyed_houses + damaged_unihabitable_houses) %>% 
  mutate(wounded_dead_100k = wounded_dead / total_pop * 100000, 
         damaged_houses_100k = damaged_houses / total_pop * 100000)

com <- read_csv("./data/com20230519.csv")

hno <- read_excel("./data/2023HNO_PiN_Severity_detailedAoI_FORSHARE 15032023.xlsx", 
                  skip = 1, 
                  sheet = 1) %>%
  clean_names() %>% 
  rename(severity = x2023_hno_inter_sector_severity) %>% 
  left_join(read_excel("./data/2023HNO_PiN_Severity_detailedAoI_FORSHARE 15032023.xlsx", 
                       skip = 1,
                       sheet = "Sector dataset") %>%
              clean_names() %>%
              select(shelter_severity:wash_severity, admin3pcode), 
            by = "admin3pcode")

eq_score <- eq %>%
  filter(!is.infinite(wounded_dead_100k) & !is.infinite(damaged_houses_100k)) %>% 
  mutate_at(vars(wounded_dead, damaged_houses, 
                 wounded_dead_100k, damaged_houses_100k), ~ range_wna(.)) %>% 
  replace_na(list(wounded_dead_100k = 0, 
                  damaged_houses_100k = 0, 
                  wounded_dead = 0, 
                  damaged_houses = 0)) %>%  
  mdepriv(c("wounded_dead", "damaged_houses", 
            "wounded_dead_100k", "damaged_houses_100k"), 
          method = "bv", output = "all", 
          score_i_heading = "eq_score")

reference_table <- com %>% 
  filter(project_status %in% c("Completed", "Ongoing") & 
           activity %out% c("ISIMM")) %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  select(admin1pcode, admin2pcode, admin3pcode, admin4pcode, 
         beneficiaries) %>% 
  left_join(com %>%
              filter(project_status %in% c("Completed", "Ongoing") &
                       activity %out% c("ISIMM")) %>%
              group_by(admin4pcode) %>% 
              summarise(beneficiary_frequencies = sum(beneficiaries, na.rm = TRUE), 
                        clusters = n_distinct(cluster, na.rm = TRUE)), 
            by = "admin4pcode") %>% 
  right_join(pop %>% select(total_pop, admin4pcode), 
             by = "admin4pcode") %>% 
  left_join(eq %>% 
              select(wounded_dead, 
                     wounded_dead_100k, 
                     damaged_houses, 
                     damaged_houses_100k, 
                     admin4pcode), 
            by = "admin4pcode") %>% 
  left_join(eq_score$data %>% 
              select(eq_score, admin4pcode), 
            by = "admin4pcode")

```

# Alternate calculations 

```{r}
eq_admin3 <- read_excel("./data/syria-earthquake-impact-20-march-2023.xlsx",
                 sheet = "DATASET") %>% 
  setNames(names_eq) %>% 
  left_join(locations %>% select(admin4pcode, admin3pcode), 
            by = c("admin4pcode")) %>% 
  mutate(wounded_dead = casualties + injuries,
             damaged_houses = completely_destroyed_houses + damaged_unihabitable_houses) %>% 
      group_by(admin3pcode) %>% 
      summarise(wounded_dead = sum(wounded_dead, na.rm = TRUE), 
                damaged_houses = sum(damaged_houses, na.rm = TRUE)) %>% 
  left_join(read_excel("./data/2023HNO_PiN_Severity_detailedAoI_FORSHARE 15032023.xlsx", skip = 1, 
                  sheet = 1) %>%
              clean_names() %>%
              select(admin3pcode, total_population, aoc = ao_c), 
            by = "admin3pcode") %>% 
  mutate(wounded_dead_100k = wounded_dead / total_population * 100000, 
         damaged_houses_100k = damaged_houses / total_population * 100000) %>% 
  mutate_at(vars(wounded_dead, damaged_houses, 
                 wounded_dead_100k, damaged_houses_100k), ~ range_wna(.)) %>% 
  mdepriv(c("wounded_dead", "damaged_houses", 
            "wounded_dead_100k", "damaged_houses_100k"), 
          method = "cz", output = "all", 
          score_i_heading = "eq_score_admin3")

alt_severity <- hno %>% 
  select(admin3pcode, shelter_severity:wash_severity) %>%
  mutate(protection_gbv_severity = as.numeric(protection_gbv_severity)) %>% 
  # All missing data replaced with 0
  replace(is.na(.), 0) %>% 
  mutate_at(vars(shelter_severity:wash_severity), ~ range_wna(.)) %>% 
  mdepriv(c("shelter_severity", "education_severity", "nutrition_severity", 
            "nfi_severity", "erl_severity", "health_severity", 
            "protection_severity", "protection_cp_severity", "protection_gbv_severity", 
            "protection_ma_severity", "food_severity", "cccm_severity", "wash_severity"), 
          method = "cz", output = "all", 
          score_i_heading = "alt_severity")

access <- 
  read_excel("C:/Users/seanywng/OneDrive/Cloud_Docs/Syria/Data Entry Form_Access Severity Syria - NWS- September 2022.xlsx",
             skip = 1, 
             sheet = "SNGOs") %>% 
  clean_names() %>% 
  rename(admin3pcode = pcode) %>% 
  mutate_at(vars(denial_of_the_existence_of_humanitarian_needs_or_of_entitlements_to_humanitarian_assistance:
                   restrictions_on_or_obstruction_of_conflict_affected_populations_access_to_services_and_assistance), 
            ~ ifelse(. == "x", 1, .)) %>% 
  replace_na(list(
    denial_of_the_existence_of_humanitarian_needs_or_of_entitlements_to_humanitarian_assistance = 0, 
    restriction_of_movement_of_agencies_personnel_or_goods_into_the_affected_country =  0, 
    restriction_of_movement_of_agencies_personnel_or_goods_within_the_affected_country = 0,
    military_operations_and_ongoing_hostilities_impeding_humanitarian_operations = 0, 
    violence_against_humanitarian_personnel_assets_and_facilities = 0, 
    interference_in_the_implementation_of_humanitarian_activities= 0, 
    presence_of_ie_ds_mines_and_ux_os = 0, 
    physical_environment = 0, 
    restrictions_on_or_obstruction_of_conflict_affected_populations_access_to_services_and_assistance = 0
  )) %>% 
  mutate_at(vars(denial_of_the_existence_of_humanitarian_needs_or_of_entitlements_to_humanitarian_assistance,
                 violence_against_humanitarian_personnel_assets_and_facilities), 
            ~ as.numeric(.))

alt_access <- access %>% 
  select(admin3pcode, 
         denial_of_the_existence_of_humanitarian_needs_or_of_entitlements_to_humanitarian_assistance:
           restrictions_on_or_obstruction_of_conflict_affected_populations_access_to_services_and_assistance) %>% 
  mdepriv(c("restriction_of_movement_of_agencies_personnel_or_goods_into_the_affected_country", 
            "restriction_of_movement_of_agencies_personnel_or_goods_within_the_affected_country", 
            "military_operations_and_ongoing_hostilities_impeding_humanitarian_operations", 
            "interference_in_the_implementation_of_humanitarian_activities", 
            "presence_of_ie_ds_mines_and_ux_os", 
            "physical_environment", 
            "restrictions_on_or_obstruction_of_conflict_affected_populations_access_to_services_and_assistance"), 
          method = "cz", output = "all", 
          score_i_heading = "alt_access")

check <- com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM" & 
           project_status %in% c("Completed", "Ongoing") & 
           beneficiaries > 0) %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  group_by(admin3pcode) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  right_join(hno %>% 
              select(admin3pcode, severity, nws_pin), 
            by = "admin3pcode") %>% 
  right_join(pop %>% 
              group_by(admin3pcode) %>% 
              summarise(population = sum(total_pop, na.rm = TRUE), 
                        .groups = "drop"), 
             by = "admin3pcode") %>% 
  left_join(com %>% 
              filter(!is.na(admin4pcode) & activity != "ISIMM" &
                       project_status %in% c("Completed", "Ongoing")) %>%
              group_by(admin3pcode) %>% 
              summarise(frequencies = sum(beneficiaries, na.rm = TRUE),
                        clusters = n_distinct(cluster, na.rm = TRUE), 
                        .groups = "drop"), 
            by = "admin3pcode") %>% 
  left_join(eq_admin3$data %>% 
              select(admin3pcode, eq_score_admin3), 
            by = "admin3pcode") %>% 
  left_join(alt_severity$data %>% 
              select(admin3pcode, alt_severity), 
            by = "admin3pcode") %>% 
  left_join(access %>% 
              select(admin3pcode, access_score = three_point_severity_score), 
            by = "admin3pcode") %>% 
  left_join(alt_access$data %>% 
              select(alt_access, admin3pcode), 
            by = "admin3pcode") %>%
  mutate(pc_reached = frequencies / population,
         coverage = beneficiaries / population)  


```


# Admin3 stuff --- think carefully about how you want to present this part
 
 
```{r}
com %>% 
  filter(activity != "ISIMM" & project_status %in% c("Completed", "Ongoing")) %>% 
  group_by(admin3pcode) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  left_join(pop %>% 
              group_by(admin3pcode) %>% 
              summarise(total_pop = sum(total_pop, na.rm = TRUE)), 
            by = "admin3pcode") %>% 
  mutate(pc_ben = beneficiaries / sum(beneficiaries), 
         pc_pop = total_pop / sum(total_pop, na.rm = TRUE)) %>% 
  rename(ben_frequencies = beneficiaries) %>% 
  mutate(`coverage%` = round(ben_frequencies / total_pop * 100, digits = 2)) %>% 
  arrange(desc(`coverage%`)) %>% 
  left_join(locations %>% 
              distinct(admin3pcode, 
                       district = admin3name_en, 
                       sub_district = admin3name_en) %>% 
              select(admin3pcode, district, sub_district), 
            by = "admin3pcode") %>% 
  select(district, 
         sub_district, 
         ben_frequencies, 
         total_pop, 
         `coverage%`)  
  filter(is.na(total_pop)) %>% 
    
  pull(sub_district)
  
  flextable() %>% 
  theme_zebra() %>% 
  set_caption("Top 20 communities with the highest number of beneficiary frequencies") %>% 
  set_table_properties(layout = "autofit", width = .99) %>% 
  fontsize(size = 10, j = 1:6, part = "header") %>% 
  fontsize(size = 9, j = 1:6)
  
pop %>% 
  distinct(admin3name_en)
  filter(admin3name_en == "Ras Al Ain")
  
locations %>% 
  filter(admin3name_en %in% c("Ras Al Ain", "Tell Abiad", "Suluk", "Ein Issa")) %>% 
  distinct(admin3pcode) %>% 
  pull(admin3pcode)
```
 

```{r}
com %>% glimpse()
  left_join(locations %>% 
              select(admin4pcode, 
                     district = admin2name_en, 
                     sub_district = admin3name_en,
                     community = location_name_en), 
            by = "admin4pcode") %>% 
  filter(activity != "ISIMM" & project_status %in% c("Completed", "Ongoing")) %>%
  filter(cluster == "FSL" & !is.na(beneficiaries) & beneficiaries > 0) %>% 
  group_by(admin4pcode) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>%
  left_join(com %>% 
              filter(activity != "ISIMM" & project_status %in% c("Completed", "Ongoing")) %>%
              group_by(admin4pcode) %>% 
              summarise(clusters = n_distinct(cluster)), 
            by = "admin4pcode") %>% 
  arrange(desc(beneficiaries)) %>%
  mutate(pc_ben = round(beneficiaries / sum(beneficiaries) * 100, digits = 2), 
         cum_pc = cumsum(pc_ben)) %>% 
  ggplot(aes(area = beneficiaries, fill = clusters)) + 
  geom_treemap() +
  geom_treemap_text(aes(label = admin4pcode), colour = "white", place = "centre", grow = TRUE) + 
  scale_fill_viridis_c(option = "mako", direction = -1,
                       breaks = c(1, 3, 6, 9)) + 
  theme(plot.caption = element_text(hjust = .5)) + 
  labs(title = "% of FSL beneficiary frequencies per community", 
       subtitle = "The top 10 communities form 45% of all beneficiary allocations", 
       caption = "Each tile is a single community. The larger the tile, the higher the share of beneficiary allocations.")
  
com %>% 
  filter(activity != "ISIMM" & project_status %in% c("Completed", "Ongoing")) %>%
  group_by(admin3pcode) %>% 
  summarise(beneficiaries = sum(beneficiaries), 
            clusters = n_distinct(cluster)) %>% 
  left_join(pop %>% 
              group_by(admin3pcode, sub_district = admin3name_en) %>% 
              summarise(total_pop = sum(total_pop, na.rm = TRUE), 
                        .groups = "drop"),
            by = "admin3pcode") %>% 
  mutate(pc_reached = beneficiaries / total_pop) %>%
  ggplot(aes(area = beneficiaries, fill = pc_reached)) + 
  geom_treemap() + 
  geom_treemap_text(aes(label = sub_district), 
                    colour = "white", 
                    place = "centre", 
                    grow = TRUE) + 
  scale_fill_viridis(labels = percent, 
                     breaks = c(1, 10, 20)) +
  theme(legend.position = "bottom") + 
  labs(fill = "% reached", 
       title = "Frequencies by sub-district") + 

com %>% 
  filter(activity != "ISIMM" & project_status %in% c("Completed", "Ongoing")) %>%
  group_by(admin3pcode) %>% 
  summarise(beneficiaries = sum(beneficiaries), 
            clusters = n_distinct(cluster)) %>% 
  left_join(pop %>% 
              group_by(admin3pcode, sub_district = admin3name_en) %>% 
              summarise(total_pop = sum(total_pop, na.rm = TRUE), 
                        .groups = "drop"),
            by = "admin3pcode") %>% 
  mutate(pc_reached = beneficiaries / total_pop) %>%
  ggplot(aes(area = total_pop, fill = pc_reached)) + 
  geom_treemap() + 
  geom_treemap_text(aes(label = sub_district), 
                    colour = "white", 
                    place = "centre", 
                    grow = TRUE) + 
  scale_fill_viridis(labels = percent, 
                     breaks = c(1, 10, 20)) +
  theme(legend.position = "bottom") + 
  labs(fill = "% reached", 
       title = "Population by sub-district") 


```


```{r}

com %>% 
  filter(activity != "ISIMM" & project_status %in% c("Completed", "Ongoing")) %>%
  group_by(admin3pcode) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE), 
            clusters = n_distinct(cluster)) %>% 
  left_join(pop %>% 
              group_by(admin3pcode) %>% 
              summarise(total_pop = sum(total_pop)), 
            by = "admin3pcode") %>% 
  left_join(eq %>% 
              left_join(locations %>% 
                          distinct(admin3pcode, admin4pcode), 
                        by = "admin4pcode") %>% 
              group_by(admin3pcode) %>% 
              summarise(wounded_dead = sum(wounded_dead), 
                        damaged_houses = sum(damaged_houses), 
                        .groups = "drop"), 
            by = "admin3pcode") %>% 
  mutate(wounded_dead_100k = round(wounded_dead / total_pop * 100000, digits = 2), 
         damaged_houses_100k = round(damaged_houses / total_pop * 100000, digits = 2), 
         pc_reached = beneficiaries / total_pop) %>%
  left_join(locations %>% 
              distinct(admin3pcode, admin3name_en), 
            by = "admin3pcode") %>% 
  rename(sub_district = admin3name_en) %>% 
  ggplot(aes(x = damaged_houses_100k, y = wounded_dead_100k)) + 
  geom_point(aes(size = beneficiaries, 
                 colour = pc_reached)) +
  geom_text_repel(aes(label = sub_district),
                   point.padding = .5, 
                   segment.color = "grey50", size = 3) +
  scale_x_log10(labels = comma) + 
  scale_y_log10(labels = comma) + 
  scale_colour_viridis(labels = percent, trans = "log") +
  #scale_size(breaks = c(0, 100, 500, 1000, 3000)) + 
  labs(x = "Number of damaged houses", 
       y = "Number of wounded and dead", 
       title = "Magnitude of earthquake impacts by sub-district", 
       subtitle = "Size shows intensity (wounded/dead per 100k) and colour shows beneficiaries", 
       size = "Wounded/dead\nper 100k", 
       colour = "Beneficiaries", 
       caption = "Data from CWG, FSL and ACU")
```


```{r}
com %>% 
  group_by(admin3pcode) %>% 
  summarise(clusters = n_distinct(cluster)) %>% 
  arrange(desc(clusters))

locations %>% 
  filter(admin3name_en == "Badama") %>% distinct(admin3pcode)

check %>% 
  filter(admin3pcode %in% c("SY070401"))

com %>% 
  filter(activity != "ISIMM" & beneficiaries > 0) %>% 
  filter(admin3pcode %in% c("SY070401")) %>% 
  group_by(cluster, activity) %>% 
  summarise(beneficiaries = sum(beneficiaries))
```


# Maps

### Severity standard

```{r fig.retina=2}
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = severity)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70", 
               trans = "log") +
  scale_fill_viridis(breaks = c(3, 4, 5)) +
  labs(title = "Severity score by sub-district") + 
  theme_void() + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = access_score)) +
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70") +
  scale_fill_viridis(breaks = c(1, 2, 3)) + 
  labs(title = "Access score by sub-district") + 
  theme_void() + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  

check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = clusters)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70", 
               trans = "log") +
  scale_fill_viridis(breaks = c(1,  3,  6, 9)) +
  theme_void() + 
  labs(title = "Number of clusters/working groups by sub-district") + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = beneficiaries)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70") +
  scale_fill_viridis(trans = "log", 
                     labels = comma,
                     breaks = c(10, 100, 1000, 10000, 100000)) +
  theme_void() +  
  labs(title = "Unique individuals reached by sub-district") + 
  theme(plot.background = element_rect(fill = "white", colour = NA))  
  

ggsave("./img/severity_standard.png", dpi = 300, height = 11.7, width = 16.5, units = "in")
  
```


```{r fig.retina=2}
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = alt_severity)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70", 
               trans = "log") +
  scale_fill_viridis() +
  labs(title = "Severity score (alternate calculation) by sub-district") + 
  theme_void() + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = alt_access)) +
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70") +
  scale_fill_viridis() + 
  labs(title = "Access score (alternate calculation) by sub-district") + 
  theme_void() + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  

check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = pc_reached)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70", 
               trans = "log") +
  scale_fill_viridis(labels = percent) +
  theme_void() + 
  labs(title = "Beneficiary frequencies as % of population by sub-district", 
       fill = "frequencies/\npopulation") + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = beneficiaries)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70") +
  scale_fill_viridis(trans = "log", 
                     labels = comma,
                     breaks = c(10, 100, 1000, 10000, 100000)) +
  theme_void() +  
  labs(title = "Unique individuals reached by sub-district") + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) 

ggsave("./img/severity_alternate.png", dpi = 300, height = 11.7, width = 16.5, units = "in")
```

### Severity frequencies

```{r fig.retina=2}
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = severity)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70", 
               trans = "log") +
  scale_fill_viridis(breaks = c(3, 4, 5)) +
  labs(title = "Severity score by sub-district") + 
  theme_void() + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = population)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70") +
  scale_fill_viridis(trans = "log", 
                     labels = comma,
                     breaks = c(10, 100, 1000, 10000, 100000, 1000000)) +
  theme_void() +  
  labs(title = "Population by sub-district") + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  

check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = pc_reached)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70", 
               trans = "log") +
  scale_fill_viridis(labels = percent, trans = "log10") +
  theme_void() + 
  labs(title = "Beneficiary frequencies as % of population by sub-district", 
       fill = "frequencies/\npopulation") + 
  theme(plot.background = element_rect(fill = "white", colour = NA)) + 
  
check %>% 
  left_join(pcode3_shape,
            by = c("admin3pcode" = "ADM3_PCODE")) %>% 
  filter(ADM1_PCODE %in% c("SY02", "SY07", "SY11") & !is.na(nws_pin)) %>% 
  st_as_sf() %>%
  ggplot() + 
  geom_sf(size = .1, colour = "grey70", 
          aes(fill = frequencies)) + 
  geom_sf_text(aes(label = ADM3_EN), size = 2, colour = "grey70") +
  scale_fill_viridis(trans = "log", 
                     labels = comma,
                     breaks = c(10, 100, 1000, 10000, 100000, 1000000)) +
  theme_void() +  
  labs(title = "Beneficiary frequencies by sub-district") + 
  theme(plot.background = element_rect(fill = "white", colour = NA))  
  

ggsave("./img/severity_frequencies.png", dpi = 300, height = 11.7, width = 16.5, units = "in")

```

```{r}

# Not a bad correlation 
# But very low R-squared

# Really there isn't enough variation in the dataset, or enough points 
check %>% 
  lm(frequencies ~ access_score, data = .) %>% 
  summary()

check %>% 
  select(access_score, frequencies) %>% 
      cor(method = "spearman", 
          use = "pairwise.complete.obs") 
```

# Correlations 

```{r}
check %>% 
  lm(pc_reached ~ alt_access, data = .) %>% 
  summary()

check %>% 
  select(alt_access, pc_reached) %>% 
      cor(method = "spearman", 
          use = "pairwise.complete.obs")

check %>% 
  lm(pc_reached ~ alt_access, data = .) %>% 
  summary()

# Not a statistically significant relationship
check %>% 
  lm(pc_reached ~ severity, data = .) %>% 
  summary()

# Fairly weak correlation too
check %>% 
  select(alt_severity, pc_reached) %>% 
      cor(method = "spearman", 
          use = "pairwise.complete.obs")

# Frequencies are extremely predictive of population 
check %>% 
  lm(frequencies ~ population, data = .) %>% 
  summary()

check %>% 
  select(population, frequencies) %>% 
      cor(method = "spearman", 
          use = "pairwise.complete.obs")
```

```{r}
com %>% 
  filter(project_status %in% c("Completed", "Ongoing") & 
           activity %out% c("ISIMM")) %>%
  group_by(admin4pcode) %>%
             slice(which.max(beneficiaries)) %>%
             ungroup() %>%
  {sum(.$beneficiaries)}

com_old %>% 
  filter(project_status %in% c("Completed", "Ongoing") & 
           activity %out% c("ISIMM")) %>%
  group_by(admin4pcode) %>%
             slice(which.max(beneficiaries)) %>%
             ungroup() %>%
  {sum(.$beneficiaries)}
```

# Admin4 dataseet

```{r}
com %>% 
  filter(project_status %in% c("Completed", "Ongoing") & 
           activity %out% c("ISIMM") & beneficiaries > 0) %>% 
  group_by(admin4pcode, cluster) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  ungroup() %>%  
  pivot_wider(names_from = cluster, values_from = beneficiaries) %>% 
  right_join(pop %>% select(total_pop, admin4pcode), 
             by = "admin4pcode") %>% 
  left_join(locations %>% 
              select(governorate = admin1name_en, 
                     district = admin2name_en, 
                     sub_district = admin3name_en, 
                     community = location_name_en, 
                     admin4pcode), 
            by = "admin4pcode") %>%
  left_join(com %>% 
              filter(project_status %in% c("Completed", "Ongoing") & 
                       activity %out% c("ISIMM")) %>%
             group_by(admin4pcode) %>%
             slice(which.max(beneficiaries)) %>%
             ungroup() %>%
             select(beneficiaries, admin4pcode), 
           by = "admin4pcode") %>% 
  mutate(beneficiaries = ifelse(beneficiaries == 0, NA_integer_, beneficiaries)) %>% 
   left_join(com %>%
              filter(project_status %in% c("Completed", "Ongoing") &
                       activity %out% c("ISIMM") & beneficiaries > 0) %>%
              group_by(admin4pcode) %>% 
              summarise(beneficiary_frequencies = sum(beneficiaries, na.rm = TRUE),
                        clusters = n_distinct(cluster, na.rm = TRUE)), 
            by = "admin4pcode") %>% 
  right_join(pop %>% select(population = total_pop, admin4pcode), 
             by = "admin4pcode") %>% 
  left_join(eq %>% 
              select(wounded_dead, 
                     wounded_dead_100k, 
                     damaged_houses, 
                     damaged_houses_100k, 
                     admin4pcode), 
            by = "admin4pcode") %>% 
  left_join(eq_score$data %>% 
              select(eq_score, admin4pcode), 
            by = "admin4pcode") %>% 
  mutate(pc_reached = beneficiary_frequencies / population, 
         pc_reached = ifelse(is.infinite(pc_reached), 
                             NA_integer_, 
                             pc_reached)) %>% 
  mutate_at(vars(wounded_dead_100k, damaged_houses_100k), 
            ~ round(., digits = 1)) %>% 
  mutate_at(vars(eq_score, pc_reached), ~ round(., digits = 3)) %>% 
  select(governorate, district, sub_district, community, admin4pcode, 
         beneficiaries, beneficiary_frequencies, clusters, eq_score, population = total_pop, pc_reached, 
         wounded_dead, wounded_dead_100k, damaged_houses, damaged_houses_100k, 
         CWG, Education, FSL, Nutrition, Protection, SNFI, WASH, CCCM, ERL) %>% 
    write_csv("./data/admin4_prioritisation.csv")
  
  

```

```{r}
com %>% 
  filter(admin4pcode %in% c("C4149")) %>% 
  group_by(cluster) %>% 
  summarise(beneficiaries = sum(beneficiaries)) %>% 
  arrange(desc(beneficiaries))



com %>% 
  filter(admin4pcode %in% c("C4148")) %>%
  filter(activity == "Multipurpose cash")
  
pop %>% filter(admin4pcode == "C4149") %>% pull(total_pop)

com %>% filter(activity == "Bread/Flour distribution" & 
                 admin4pcode == "C4141") 

com %>% glimpse()
```



# Unused code from report

### Number of unique individuals reached 

The total number of unique individuals that has been reached by the response so far is `r filter(com, !is.na(admin4pcode)) %>% group_by(admin4pcode) %>% slice(which.max(beneficiaries)) %>% ungroup() %>% {sum(.$beneficiaries)} %>% format(big.mark = ",")` persons. 

```{r}
com %>% 
  filter(cluster == "CCCM") %>% 
  count(activity, sort = TRUE)
```

alternative calculation for unique individuals 
frankenstein column called site 

Whether it is better to calculated individuals using "site", a made up column or by admin4, which leads to significant undercounting. 

Kick this issue to the OCHA IM unit for decision. 

```{r}

com  %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>%
  group_by(site) %>% 
  slice(which.max(beneficiaries)) %>% 
  {sum(.$beneficiaries, na.rm = TRUE)}

```




```{r}
com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  {sum(.$beneficiaries)} %>% format(big.mark = ",")

com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  group_by(admin4pcode) %>% 
  summarise(ben_freq = sum(beneficiaries)) %>% 
  left_join(pop %>% select(admin4pcode, total_pop), 
            by = "admin4pcode") %>% 
  mutate(pc = ben_freq / total_pop) %>% 
  ggplot(aes(x = total_pop, y = ben_freq)) + 
  geom_point(aes(size = pc)) + 
  scale_x_log10() + 
  scale_y_log10()
  
```


```{r}
com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  group_by(admin4pcode) %>% 
  summarise(ben_freq = sum(beneficiaries)) %>% 
  left_join(pop %>% select(admin4pcode, total_pop), 
            by = "admin4pcode") %>% 
  mutate(pc = ben_freq / total_pop) %>% 
  ggplot(aes(x = pc, y = ben_freq)) + 
  geom_point(aes(size = pc), 
             alpha = .5) + 
  scale_x_log10(labels = percent) + 
  scale_y_log10(labels = comma)
```

```{r}
reached_100 <- com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  summarise(ben_freq = sum(beneficiaries), 
            clusters = n_distinct(cluster),) %>% 
  left_join(pop %>% select(admin4pcode, total_pop, 
                           governorate = admin1name_en, 
                           sub_district = admin3name_en, 
                           community = admin4name_en), 
            by = "admin4pcode") %>% 
  mutate(pc = ben_freq / total_pop) %>% 
  filter(pc > .99) %>% 
  pull(admin4pcode)

pop %>% glimpse()
```


```{r}
com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(site) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  group_by(admin4pcode) %>% 
  summarise(ben_freq = sum(beneficiaries)) %>% 
  left_join(pop %>% select(admin4pcode, total_pop), 
            by = "admin4pcode") %>% 
  mutate(pc = ben_freq / total_pop) %>%
  ggplot(aes(x = pc)) + 
  geom_histogram() + 
  scale_x_log10(labels = percent) + 
  labs(x = "Percent of population covered")
```

Histogram by site 

```{r}
com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(site) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  group_by(admin4pcode) %>% 
  summarise(ben_freq = sum(beneficiaries)) %>% 
  left_join(pop %>% select(admin4pcode, total_pop), 
            by = "admin4pcode") %>% 
  mutate(pc = ben_freq / total_pop) %>%
  ggplot(aes(x = pc)) + 
  geom_histogram() + 
  scale_x_log10(labels = percent) + 
  labs(x = "Percent of population covered")
```


Export a list of communities that are heavily oversubscribed and also communities that are very undersubscribed 


The Cash Working Group is interested in the following indicators: 

* The percentage of individuals who have received cash assistance of any kind
* The percentage of individuals who have received multi-purpose cash assistance 
* The percentage of beneficiary frequencies, per cluster and per activity, who have received cash assistance 

Site-level data is necessary for any of these calculations to take place. And the calculation of the number of unique individuals reached is an important figure to all clusters. However, the CWG has no interest in imposing its reporting policy and calculations on other clusters -- this section instead outlines how the CWG intends to process these figures, to document them for public knowledge and for ease of future revision. 

To reiterate, the multi-sector reached has been calculated according to the CWG's own preferences (please download the code to see the exact conditions). Other coordination bodies and clusters should make their own determinations. 

Site-level data is important in calculating the number of unique individuals reached -- this itself is an important figure for the CWG as we work to determine the percentage of beneficiaries who have received assistance through in-kind, cash or service delivery modalities. 

Unique individuals are distinct from beneficiary frequencies -- a family of four receiving cash assistance, hygiene kits and emergency shelter kits represent 12 beneficiary frequencies, but are 4 unique individuals. 

Beneficiary frequencies can be easily determined by summing beneficiaries reached regardless or whether they have been reached before. 

The ideal way to determine the number of unique individuals reached is through an established and maintained beneficiary database. However, this option is not available to us. Whilst various clusters may have different formulae for calculating individuals reached, common approaches include a column asking whether beneficiaries have been previously assisted or taking the highest number reached out of any activity per community then summing those together. 

This second option -- taking the highest number reached, by any activity, at site level -- is the best available option to avoid double counting. In fact, there will be usually be some slight undercounting. However, site-level consolidation is not currently an option. The lowest-common denominator between clusters is the community level, or admin4 (with the very notable exception of Health, which only reports at admin3, likely due to the catchment area of each health facility). 

Site-level (camp, specific location in the community) data is only collected in the following templates:

* WASH: camp pcodes and the specific WASH installations are collected
* FSL: camp pcodes are collected
* Education: camp pcodes and names are available, as are schools and their unique identifier numbers.
* Nutrition: camp pcodes are collected, health facility names and school names are collected. 
* Protection: camp pcodes are collected
* Cash: camp pcodes are collected

However, as will be explored in the following sections, site-level data (admin5) is of quite poor quality, largely due to the poor standardisation of site names, differing thoughts on the ownership of the geoadmins dataset as well as due to a lot of information not being collected. Therefore, pushing everyone down to reporting at admin5 without first resolving these issues would be a lot of effort for very marignal gains. 


<br><br> 

### Coordination and multi-sector footprint

```{r}

com %>% 
  group_by(cluster, admin4pcode) %>% 
  summarise(count = n()) %>% 
  pairwise_cor(cluster, admin4pcode, value = count, 
               method = c("spearman"), upper = FALSE) %>% 
  arrange(desc(correlation))

com %>% 
  group_by(activity, admin4pcode) %>% 
  summarise(count = n()) %>% 
  pairwise_cor(activity, admin4pcode, value = count, 
               method = c("spearman"), upper = FALSE) %>% 
  arrange(desc(correlation)) %>% 
  left_join(com %>% 
              distinct(cluster1 = cluster, activity), 
            by = c("item1" = "activity")) %>% 
  left_join(com %>% 
              distinct(cluster2 = cluster, activity), 
            by = c("item2" = "activity")) %>% 
  filter(cluster1 != cluster2)

com %>%
  filter(!is.na(admin4pcode) & !is.na(activity)) %>% 
  pairwise_count(activity, admin4pcode, sort = TRUE)


```

All this being said, the consolidation of the 4W data does create additional opportunities 

The consolidation of this 4W data creates additional opportunities for inter-cluster coordination. Inter-cluster coordination is not the purview of the Cash Working Group and OCHA is more than capable to making these opportunities for themselves. 

However, it would also be remiss to not mention what new metrics would be available for analysis: 

* The number of clusters per admin4 (useful for determining inter-cluster gaps i.e. are there any areas where we are doing education without shelter? Nutrition without food security?)
* The number of activities per admin4 (similar to above, but more detailed)
* The number of beneficiary frequencies at admin4 (collectively, what has been the level of investment in each community by the humanitarian community as a whole? Important for determining if allocations have been fair i.e. are there communities of similar pre-existing vulnerability and earthquake damage that have received drastically different levels of support?)

Again, inter-cluster coordination is not the purview of the Cash Working Group, but we are happy to share all the code and data with whoever wants to take the lead for that. 

### Population 

```{r}

# Number of communities reached so far 
com %>%
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>%
  summarise(communities = n_distinct(admin4pcode))
  
  
```

The issue with calculating these metrics is that we do not have an intercluster target. 

Calculating all these metrics is pretty academic unless coordination wants to do something about it. 

```{r}
pop %>% 
  filter(admin3pcode %in% nw_pcode3) %>% 
  {mean(.$total_pop)}
```


```{r}
com %>% 
  left_join(pop %>% 
              select(total_pop, admin4pcode), 
            by = "admin4pcode") %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE), 
            population = sum(total_pop, na.rm = TRUE)) %>% 
  mutate(pc_reached = round(beneficiaries / population * 100, digits = 2))
```



```{r}
com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  summarise(sectors = n_distinct(cluster)) %>% 
  ggplot(aes(x = sectors)) + 
  geom_histogram(bins = 9) + 
  scale_x_continuous(breaks = seq(1, 9, by = 1)) + 
  geom_text(stat = "count", aes(label=..count..), vjust= - 0.5) +
  expand_limits(y = 260) + 
  labs(x = "Number of sectors", 
       y = "Number of communities", 
       title = "245 communities only have one cluster present")
```
<br>

```{r}
com %>% 
  filter(cluster == "FSL") %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  {sum(.$beneficiaries, na.rm = TRUE)}

pop %>% 
  count(admin1pcode)
  glimpse()
```


```{r}
com %>% 
  filter(!is.na(admin4pcode) & activity != "ISIMM") %>% 
  group_by(admin4pcode) %>% 
  summarise(sectors = n_distinct(cluster)) %>% 
  filter(sectors == 1)
```


We note, from the table below, that the single cluster present in most of these 774 communities is CCCM.

```{r}
com %>% 
  # Should water quality testing be included? 
  filter(!is.na(admin4pcode)  & activity %out% c("ISIMM")) %>% 
  group_by(cluster) %>% 
  summarise(ben_frequencies = sum(beneficiaries, na.rm = TRUE), 
            communities = n_distinct(admin4pcode)) %>% 
  arrange(desc(communities)) %>% 
  flextable() %>% 
  theme_zebra() %>% 
  set_caption("Footprint and reach per cluster/WG") %>% 
  footnote(i = 1, j = 2, inline = TRUE, ref_symbols = "1", part = "header",
           as_paragraph("Beneficiary frequencies are the number of times an individual has received assistance, regardless double counting")) %>% 
  set_table_properties(layout = "autofit", width = .7)
```

<br>

```{r}
com %>% 
  filter(cluster == "WASH") %>% 
  group_by(activity) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  arrange(desc(beneficiaries))
```


Following CCCM, FSL has the largest footprint. SNFI and ERL have markedly more concentrated footprints. This probably has implications for the earthquake response as it will necessarily focused around Shelter. 


<br>

There are 34 communities where the only cluster present is not CCCM. In the majority of these cases, the single cluster present is either Education or Nutrition. 

Export a csv of all communities which only have one cluster operating. 

```{r}
com %>% 
  filter(!is.na(admin4pcode) ) %>% 
  group_by(admin4pcode, cluster) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = cluster, values_from = beneficiaries) %>%
  mutate(clusters = rowSums(!is.na(.[,-1]))) %>% 
  {mean(.$clusters, na.rm = TRUE)}

com %>% 
  filter(!is.na(admin4pcode) ) %>% 
  group_by(admin4pcode, cluster) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = cluster, values_from = beneficiaries) %>%
  mutate(clusters = rowSums(!is.na(.[,-1]))) %>% 
  ummarise(cash = sum(!is.na(Cash)), 
            education = sum(!is.na(Education)), 
            fsl = sum(!is.na(FSL)), 
            nut = sum(!is.na(Nutrition)), 
            prot = sum(!is.na(Protection)), 
            snfi = sum(!is.na(SNFI)), 
            wash = sum(!is.na(WASH)), 
            erl = sum(!is.na(ERL)), 
            cccm = sum(!is.na(CCCM)), 
            edu = sum(!is.na(Education)))
  filter(clusters == 1 & is.na(CCCM))
  
  filter(admin4pcode %in% reached_100) %>% 
  {mean(.$clusters, na.rm = TRUE)}


  summarise(cash = sum(!is.na(Cash)), 
            education = sum(!is.na(Education)), 
            fsl = sum(!is.na(FSL)), 
            nut = sum(!is.na(Nutrition)), 
            prot = sum(!is.na(Protection)), 
            snfi = sum(!is.na(SNFI)), 
            wash = sum(!is.na(WASH)), 
            erl = sum(!is.na(ERL)), 
            cccm = sum(!is.na(CCCM)), 
            edu = sum(!is.na(Education)))
  filter(clusters == 1 & is.na(CCCM))
  
```




Multi-sector coverage is generally much better in Idleb than Aleppo. 

Was this intentional? 



```{r}
com %>% 
  filter(activity != "ISIMM") %>% 
  filter(admin1pcode %in% c("SY02", "SY07")) %>% 
  group_by(admin1pcode, admin4pcode) %>% 
  summarise(clusters = n_distinct(cluster)) %>%
  ggplot(aes(x = clusters)) + 
  geom_histogram(bins = 10) + 
  facet_wrap(~ admin1pcode) + 
  scale_x_continuous(breaks = seq(0, 9, by = 1))
  
```

```{r}
aleppo_one_cluster <- com %>% 
  filter(activity != "ISIMM" & admin1pcode == "SY02") %>% 
  group_by(admin4pcode) %>% 
  summarise(clusters = n_distinct(cluster)) %>% 
  filter(clusters == 1) %>% 
  pull(admin4pcode)
  
```

```{r}
com %>% 
  filter(!is.na(admin4pcode) ) %>% 
  group_by(admin4pcode, cluster) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = cluster, values_from = beneficiaries) %>%
  mutate(clusters = rowSums(!is.na(.[,-1]))) %>%  
  filter(admin4pcode %in% aleppo_one_cluster) %>% 
  summarise(cash = sum(!is.na(Cash)), 
            education = sum(!is.na(Education)), 
            fsl = sum(!is.na(FSL)), 
            nut = sum(!is.na(Nutrition)), 
            prot = sum(!is.na(Protection)), 
            snfi = sum(!is.na(SNFI)), 
            wash = sum(!is.na(WASH)), 
            erl = sum(!is.na(ERL)), 
            cccm = sum(!is.na(CCCM)), 
            edu = sum(!is.na(Education)))
```

No real pattern as to why there are so many communities with only one cluster operational in Aleppo. 

Main offender is FSL. 

75 communities in Aleppo with only FSL. Maybe WFP has a giant contract for Aleppo and is forcing people to work there, without other clusters present. 


```{r}
com %>% 
  pairwise_count(cluster, admin4pcode, upper = FALSE) %>% 
  arrange(desc(n))

com %>% 
  pairwise_cor(cluster, admin4pcode, method = "spearman", 
               sort = TRUE, upper = FALSE) 
```

Does Education work in camps? 
Programmatically all ERL areas should have been covered in the emergency phase by other actors. 
Pretty low overlap between Shelter and WASH.
Ask what Nutrition and FSL are doing to coordinate

What is the number of multisector beneficiaries per pair? 

Focus a bit more on SNFI and ERL footprints. 


```{r}

com %>% filter(!is.na(camp_name) & is.na(admin5pcode)) %>% 
  summarise(camp_no_code = n_distinct(camp_name), 
            ben_freq = sum(beneficiaries, na.rm = TRUE)) %>% 
  flextable() %>% 
  theme_zebra()
  
```

<br><br>


### Beneficiary disaggregations 



<br><br><br>

### Modalities 

```{r}
glimpse(wash)

wash %>% filter(!is.na(cash_hk)) %>% 
  count(cash_hk)
```


4.82% of all beneficiary frequencies received cash assistance 

```{r}
com %>% 
  count(delivery_modality, sort = TRUE)

com %>% 
  filter(activity != "ISIMM") %>% 
  filter(project_status %in% c("Completed", "Ongoing")) %>% 
  mutate(cash_ben = ifelse(delivery_modality == "Cash", 
                           beneficiaries, 
                           0)) %>% 
  group_by(month) %>% 
  summarise(cash_ben_freq = sum(cash_ben, na.rm = TRUE), 
            ben_freq = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(cash_pc = round(cash_ben_freq / ben_freq * 100, digits = 2))

# Unique individuals who received cash 
com %>% 
  mutate(cash_ben = ifelse(delivery_modality == "Cash", 
                           beneficiaries, 
                           0)) %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(cash_ben)) %>% 
  {sum(.$cash_ben, na.rm = TRUE)}

com %>% 
  filter(month == "FEB") %>% 
  distinct(cluster)
```

Significant monetisation of in-kind activities during winterisation, but...

WASH not having delivery modalities is due to the abnormal structure of their 4Ws -- but they must have a codebook somewhere? Same with CCCM 

Nutrition activities without the delivery modality can easily be backfilled, given the clear definition of their activities, but that's for the Nutrition IMO to do.


## Lack of documentation for 4Ws

Given the high turnover in IMs and general response staff, it would be helpful to have codebooks for each of the 4Ws. 

There are limits to what we can do in this document -- this is merely a review, not a formal codebook. Even if I made one, it would only be for cash. 

```{r}
com %>% 
  filter(is.na(delivery_modality) & cluster == "Nutrition") %>% 
  group_by(activity) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE))
```


## Admin5/Master list of locations 

Cleaning out the admin5 is a priority. 
There needs to be a master location list of not just camps, but sites, consolidating schools, health facilities and so on. 

There has to be standardisation in the names of camps and someone has to take ownership for the camps not managed by CCCM. 

There are, consistently camps that partners are working in, but there is no code for. 

Ideally, the owner of the master list of locations would be OCHA, since it does not only include camps. 

The inclusion of site data will also allow us to define better, the number of unique individuals reached. 

I think we just have to use the romanised English names when we standardise locations, just for easier reading into digital formats.

As long as the admin5 are not cleaned out, it makes no sense for us to ask clusters lke SNFI or ERL to report at admin5 because we don't get any value from it. 


```{r}
com %>% 
  filter(!is.na(camp_name) & is.na(admin5pcode)) %>% 
  summarise(no_code_camps = n_distinct(camp_name))

com %>% filter(!is.na(camp_name))
```

No consistency in codes or names of sites -- cf nutrition health facility names and WASH facility names 

Education does not provide school names -- is this an anonymisation issue?
WASH does provide the actual names of schools -- 211 of them, even 



```{r}
com %>% 
  mutate(no_admin5 = ifelse(is.na(admin5pcode), 
                            "yes", 
                            "no")) %>% 
  filter(activity != "ISIMM") %>% 
  group_by(cluster, no_admin5) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  pivot_wider(names_from = no_admin5, values_from = beneficiaries) %>% 
  mutate(total_frequencies = sum(yes, no, na.rm = TRUE), 
         pc_missing = round(yes / total_frequencies * 100, digits = 2)) %>% 
  select(-total_frequencies) %>% 
  flextable() %>% 
  theme_zebra() %>% 
  set_caption("The impracticality of requiring partners to report at admin5") %>% 
  set_table_properties(layout = "autofit", width = .8)
  
```


### Activities

```{r}
com %>% 
  filter(project_status %in% c("Completed", "Ongoing")) %>% 
  
```


```{r}
com %>% 
  group_by(cluster, admin4pcode) %>% 
  summarise(count = n()) %>% 
  pairwise_cor(cluster, admin4pcode, value = count, 
               method = c("spearman"), upper = FALSE) %>% 
  arrange(desc(correlation))

com %>% 
  filter(project_status %in% c("Completed", "Ongoing") & 
           activity != "ISIMM") %>% 
  group_by(activity, admin4pcode) %>% 
  summarise(count = n()) %>% 
  pairwise_cor(activity, admin4pcode, value = count, 
               method = c("spearman"), upper = FALSE) %>% 
  arrange(desc(correlation)) %>% 
  left_join(com %>% 
              distinct(cluster1 = cluster, activity), 
            by = c("item1" = "activity")) %>% 
  left_join(com %>% 
              distinct(cluster2 = cluster, activity), 
            by = c("item2" = "activity")) %>% 
  filter(cluster1 != cluster2)

com %>% 
  filter(project_status %in% c("Completed", "Ongoing") & 
           activity != "ISIMM") %>% 
  pairwise_count(activity, admin4pcode, sort = TRUE, upper = FALSE) %>% 
  left_join(com %>% 
              distinct(cluster1 = cluster, activity), 
            by = c("item1" = "activity")) %>% 
  left_join(com %>% 
              distinct(cluster2 = cluster, activity), 
            by = c("item2" = "activity")) %>% 
  filter(cluster1 != cluster2)
```

```{r}
nut %>% 
  count(activity, sort = TRUE)

nut %>% 
  mutate(activity = str_remove_all(activity, "(6  59 months) | for six months| for four month|"), 
         activity = str_replace_all(activity, 
                                    " who received micronutrients, including iron, folate ", 
                                    "received micronutrrients"), 
         )
```






```{r eval=FALSE}

# WASH being problematic
wash %>%
    pivot_longer(cols = c(rehab_repair_water_station, 
                          o_m, 
                          construction_water_station, 
                          network_rehab, 
                          construction_water_network, 
                          chlorination, 
                          wq_testing, 
                          fuel_consumption, 
                          water_safety_plans, 
                          water_trucking, 
                          cash_assistance_water_trucking, 
                          pvt_boreholes, 
                          cash_assistance_private_boreholes, 
                          tanks_pwd_ben, 
                          hh_water_treatment, 
                          hh_water_treatement_cash_assistance, 
                          sew_rehab_repair, 
                          sew_support, 
                          sew_construction, 
                          beneficiaries_toilets, 
                          pw_d_beneficiaries_toilet, 
                          beneficiaries_cash_toilets, 
                          bath_new, 
                          cash_bath,
                          des_beneficiaries, 
                          swm_support_benf, 
                          hp_ben, 
                          hp_pwd_ben, 
                          hk_ben, 
                          cash_hk, 
                          pwd_beneficiaries, 
                          wash_nfi_ben, 
                          incinerator_health_facilities, 
                          cholera_safe_water, 
                          chlorin_cholera, 
                          cholera_sew, 
                          cholera_kit, 
                          cholera_hp_rcce_iec, 
                          cholera_wash_in_health), 
                 names_to = "activity", values_to = "beneficiaries") %>% 
  # A bit controversial, but if I don't do this, WASH will be gigantic
  # group_by(activity, admin4pcode) %>% 
  # slice(which.max(beneficiaries)) %>% 
  # ungroup() %>% 
    mutate(delivery_modality = NA_character_,
           cluster = "WASH") %>% 
  group_by(activity) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  arrange(desc(beneficiaries))

com %>% count(project_status)


```

WASH des_beneficiaries is almost certainly disinfection or desinfeccion. However, this still doesn't allow me to remove beneficiaries from the totals, so WASH numbers will continue to be inflated, 

# 3. Calculations for OCHA reporting 

This section is mostly outdated. Please refer to the rmd `cluster_calculations` for the documentation.  

### Monthly

```{r}
rbind(
  
  wash %>% 
  filter(project_status == "Completed") %>% 
  mutate(month = str_to_lower(month)) %>% 
  group_by(month, 
           health_facility_name, 
           school_name, 
           collective_shelter_name, 
           admin5pcode, 
           admin4pcode) %>%
  slice(which.max(so2)) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(so2, na.rm = TRUE)) %>% 
  mutate(type = "wash_monthly"), 
  
  cccm %>% 
  filter(activity == "CCCM") %>% 
  pivot_longer(cols = (jan:dec), names_to = "month", values_to = "beneficiaries") %>% 
  group_by(admin4pcode, month) %>%
  slice(which.max(beneficiaries)) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "cccm_monthly"), 
  
  erl %>%  
  mutate(month = str_sub(implementing_month, start = 5L, end = 7L), 
         month = str_to_lower(month)) %>% 
  filter(report_this_to_any_other_sector == "No") %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "erl_monthly"), 
  
  health %>% 
  mutate(month = case_when(implementation_month == 1 ~ "jan", 
                           implementation_month == 2 ~ "feb", 
                           TRUE ~ NA_character_)) %>% 
  filter(!is.na(month)) %>% 
  group_by(month) %>% 
  filter(activity == "medical_procedures") %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "health_monthly"), 
  
  fsl %>% 
  filter(activity == "Food Baskets" & reported_to_other_sector == "No") %>% 
  mutate(month = str_to_lower(str_sub(reporting_month, start = 1L, end = 3L))) %>%
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "food_monthly"), 
  
  cash %>% 
  filter(project_status == "Completed") %>% 
  group_by(month = month(distribution_date, label = TRUE)) %>% 
  filter(!is.na(month)) %>% 
  mutate(month = str_to_lower(month)) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "cash_monthly"), 
  
  snfi %>% filter(cluster == "nfi" & activity == "1.1.1.1: Provision of core NFIs" & 
                  new_beneficiaries == "Yes") %>% 
  mutate(month = str_to_lower(str_sub(reporting_month, start = 1L, end = 3L))) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "nfi_monthly"), 

  snfi %>% 
  filter(cluster == "shelter" & new_beneficiaries == "Yes") %>% 
  mutate(month = str_to_lower(str_sub(reporting_month, start = 1L, end = 3L))) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "shelter_monthly")
  
) %>% 
  arrange(type, month) %>% 
  write_csv("./data/monthly_by_cluster.csv")
```



### Cash 

```{r}
cash %>% 
  filter(project_status == "Completed") %>% 
  group_by(month = month(distribution_date, label = TRUE)) %>% 
  filter(!is.na(month)) %>% 
  mutate(month = str_to_lower(month)) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "cash_monthly")


  
```


### WASH 



Total reached is just the `so2` column 
We also calculate `so1` for comparison  

You need to do this for s01 and s02
Monthly: Max -- health facility OR school, collective shelter, camp_code, community
Cumulative is the max of all months, for the same levels, starting with health facility OR school

```{r warning = FALSE}

# Monthly reached
wash %>% 
  filter(project_status == "Completed") %>% 
  group_by(month, 
           health_facility_name, 
           school_name, 
           collective_shelter_name, 
           admin5pcode, 
           admin4pcode) %>%
  slice(which.max(so2)) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(so2, na.rm = TRUE)) %>% 
  mutate(type = "wash_monthly")

# Cumulative
# The cumulative tallies
wash %>% 
  filter(project_status == "Completed") %>% 
  group_by(health_facility_name, 
           school_name, 
           collective_shelter_name, 
           admin5pcode, 
           admin4pcode) %>%
  slice(which.max(so2)) %>% 
  ungroup() %>% 
  summarise(beneficiaries = sum(so2, na.rm = TRUE)) %>% 
  mutate(type = "wash_cumulative")

# so1 calculations 
# These tally 
wash %>% 
  filter(project_status == "Completed") %>% 
  group_by(health_facility_name, 
           school_name, 
           collective_shelter_name, 
           camp_name, 
           admin5pcode, 
           admin4pcode) %>%
  slice(which.max(so1_1_1)) %>% 
  ungroup() %>% 
  summarise(beneficiaries = sum(so1_1_1, na.rm = TRUE)) %>% 
  mutate(type = "wash_so1_1_1_cumulative")


wash %>% 
  filter(project_status == "Completed") %>% 
  group_by(health_facility_name, 
           school_name, 
           collective_shelter_name, 
           camp_name, 
           admin5pcode, 
           admin4pcode) %>%
  slice(which.max(so1_1_2)) %>% 
  ungroup() %>% 
  summarise(beneficiaries = sum(so1_1_2, na.rm = TRUE)) %>% 
  mutate(type = "wash_so1_1_2_cumulative")
```


```{r eval=FALSE}
wash %>% 
  filter(project_status == "Completed" & !is.na(ngo_code)) %>% 
   select(
         electrical_bills, 
         cash_assistance_water_trucking,
         cash_assistance_private_boreholes,
         hh_water_treatement_cash_assistance, 
         beneficiaries_cash_toilets, 
         cash_bath, 
         cash_hk, 
         cash_wash_nfi,
         cash_total_money_usd) %>%
  filter(!is.na(cash_assistance_water_trucking))
  count(cash_assistance_private_boreholes)
```


<br>

WASH has multiple cash-response activities, including assistance with electric bills, cash assistance for water trucking and even subsidies for toilet construction. 

However, their 4Ws is missing most of the quality and design-related columns, such as conditionality and cash delivery mechanism. The CWG is strongly encouraged to advocate for the necessary changes to WASH's template. 

<br><br><br>

### CCCM        

two figures reported: 
assisted IDPs (CCCM assisted, ignore ISIMM sheet), 
tracked IDPs (tracked, submitted separately)

cumulative is the max across months -- for the assisted IDPs (new arrivals sheet)
new arrivals individuals -- the cumulative is the sum, as these are population movements 

For the dashboard:
we are currently reliant on calculations for the dashboard
raw data currently not provided to OCHA NWS





```{r}

cccm %>% 
  filter(activity == "CCCM") %>% 
  pivot_longer(cols = (jan:dec), names_to = "month", values_to = "beneficiaries") %>% 
  group_by(admin4pcode) %>%
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "cccm_cumulative")

cccm %>% 
  filter(activity == "CCCM") %>% 
  pivot_longer(cols = (jan:dec), names_to = "month", values_to = "beneficiaries") %>% 
  group_by(admin4pcode, month) %>%
  slice(which.max(beneficiaries)) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "cccm_monthly")

```
  


It is not currently possible to integrate CCCM's 4W submissions into an inter-cluster template. However, it is also unclear if any of CCCM's activities have cash components. 

It is unlikely that the template provided to OCHA for reporting purposes is the actual template being used inside CCCM -- a data-sharing agreement will need to be reached in order for the CWG to fully understand the data that CCCM is managing. 

<br><br><br> 

### Shelter

- unique beneficiaries: use new beneficiary column 

NFI uses 1.1.1.1: Provision of core NFIs for the monthly reached, and for the cumulative, but use new beneficiary column -- unique calculation to be confirmed. 

SNFI disaggregations -- girls, boys, men, women, elderly men, elderly women 

Shelter takes all beneficiaries of all activities, for the unique, we use the new beneficiary column 


```{r}
# NFI reached 
snfi %>% filter(cluster == "nfi" & activity == "1.1.1.1: Provision of core NFIs" & 
                  new_beneficiaries == "Yes") %>% 
  mutate(month = str_to_lower(str_sub(reporting_month, start = 1L, end = 3L))) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "nfi_monthly")

snfi %>% 
  filter(cluster == "shelter" & new_beneficiaries == "Yes") %>% 
  mutate(month = str_to_lower(str_sub(reporting_month, start = 1L, end = 3L))) %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "shelter_monthly")
  
  {sum(.$beneficiaries, na.rm = TRUE)}

```




The Shelter/NFI 4Ws are almost interoperable with the CWG 4Ws, containing columns on the delivery modality (cash, in-kind and voucher), cash conditionality, the transfer value per household and the cash delivery mechanism. However, payment frequency is missing. 

```{r eval=FALSE}
snfi %>% 
  filter(delivery_modality != "END_OF_FORMULA") %>% 
  group_by(delivery_modality, cash_delivery_mechanism) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) 
```

Shelter has quite a good list of cash delivery mechanism options:
-Cash-for-work
-Direct cash payment
-E-transfer
-Money transfer agent
-Paper voucher
-Other


### Health 

The data for the previous month usually changes 

For calculation of beneficiaries reached:
 
-medical_procedures 
cluster reached is medical_procedures

treatment is used to compared to the Amman 

-x1_5_1_treatment_courses_delivered_to_health_facilities_drug_treatment_one_

so health uses sub_district for beneficiary calculations

separate columns
for presentation in the dashboard: 
x1_1_1_outpatients_cons
x1_1_7_cases_referred_specialized_treatment_inside_syria_cross_line_and_cro
x1_1_3_mental_health_cons_supported   
x1_1_4_physical_rehab_sess_supported

sex and age disaggregation, just the MSNA percentages -- 19%, 24%, 30%, 27%
girls, boys, women, men

cumulative: sum of all months (frequencies), interventions as opposed to persons 


```{r}

health %>% 
  mutate(month = case_when(implementation_month == 1 ~ "jan", 
                           implementation_month == 2 ~ "feb", 
                           TRUE ~ NA_character_)) %>% 
  filter(!is.na(month)) %>% 
  group_by(month) %>% 
  filter(activity == "medical_procedures") %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "health_monthly")
  {sum(.$beneficiaries, na.rm = TRUE)}

health %>% glimpse()
```

Health 4Ws are useful contain community pcodes and are therefore interoperable from a geographic coverage and gaps standpoint. However, the template lacks key columns necessary for cash analysis. A `delivery modality` column exists, but has no options. There are no columns for conditionality or dollar value of interventions. 

### ERL

Report on both direct and indirect beneficiaries 

For the monthly reached, only direct beneficiaries not reported to other clusters
For the the cumulative, only direct beneficiaries and not previously assisted and not reported to other clusters. 

disaggregations are backfilled so they can be ignored. 



```{r}

# Monthly reached
erl %>%  
  mutate(month = str_sub(implementing_month, start = 5L, end = 7L), 
         month = str_to_lower(month)) %>% 
  filter(report_this_to_any_other_sector == "No") %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "erl_monthly")

# Cumulative
erl %>%  
  mutate(month = str_sub(implementing_month, start = 5L, end = 7L)) %>% 
  filter(report_this_to_any_other_sector == "No" & previously_assisted == "No") %>% 
  # These steps are not necessary
  # group_by(admin4pcode) %>% 
  # slice(which.max(beneficiaries)) %>% 
  # ungroup() %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE))
```

```{r}


erl %>% glimpse()
```

```{r eval=FALSE}
erl %>% 
  filter(delivery_modality == "Cash") %>% 
  count(indicator_unit)
  group_by(deliver_mechanism = if_cash_cash_delivery_mechanism) %>% 
  summarise(beneficiaries = sum(total_beneficiaries) )
  
erl %>% 
  count(report_this_to_any_other_sector)
```


ERL 4Ws are fully interoperable with CWG's 4Ws. Delivery modality is available, so is conditionality, frequency of distribution, delivery mechanism and transfer value per household. 

Unique beneficiaries are available, with a separate column,

ERL and FSL are the only clusters to ask if data has been reported to other Clusters. Whilst still not 


### FSL 

#### Food 
-food baskets for the monthly reached, filtered from `fss_activity_do_not_write`

-Total beneficiaries assisted: `beneficiaries`

-For the monthly reached, `beneficiaries` 
-For the cumulative, AVERAGE of beneficiaries at community level, for some reason FSL is using sub-district 
-For their their averages, they are dividing only dividing by the months that have beneficiaries, essentially na.rm = TRUE

#### Livelihoods

-all non-food activities, excluding cash-for-work 
-For the cumulative is the SUM 

females is total females, so adult women you have to subtract the girls from the female total; same for males 

UN/non-UN are provided separately


```{r}

# Food Monthly reached 
fsl %>% 
  filter(activity == "Food Baskets" & reported_to_other_sector == "No") %>% 
  group_by(reporting_month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE))

# Food Cumulative
fsl %>% 
  mutate(month = case_when(reporting_month == "January" ~ "jan", 
                           TRUE ~ NA_character_)) %>% 
  filter(activity == "Food Baskets" & reported_to_other_sector == "No") %>% 
  group_by(final_implementing_partner, admin4pcode) %>% 
  slice(which.max(beneficiaries)) %>% 
  ungroup() %>% 
  group_by(month) %>% 
  summarise(beneficiaries = sum(beneficiaries, na.rm = TRUE)) %>% 
  mutate(type = "food_cumulative")
  {sum(.$beneficiaries)}

```

```{r}
fsl %>% glimpse()
```



FSL's template, unsurprisingly, is also in full alignment with standard cash reporting standards and there will be no problems integrating their data into the Cash 4Ws. FSL 4Ws are fully interoperable.  

<br><br><br>

### Education 

-Monthly reached is sum of all activities 
-Cumulative is the sum of all the months 

Data calculation table is wrong. But we can only use the data calculation sheet. Education hasn't provided how their beneficiaries are calculated from raw data 

For fun, just calculate the max by school, adults and children 

Education disaggregations are provided

```{r}
edu %>% 
  
```


```{r}

edu %>% glimpse()

```


Education has at least two activities with cash components: 

* *1.07.12 Provide maintenance and running costs, including cleaning material, stationery*`*
* *2.02.2 Provide teachers and education personnel with monetary and non-monetary incentives. This including, pre-paid cards/vouchers, transportation allowance, financial payment, etc. to carry out education services in non-formal settings*

There is nowhere in the template to record either the amount of funding disbursed, the frequency or any of the other associated cash-reporting columns. The Education 4Ws, in their current form, are not interoperable with the CWG's template at all, though they can still be used to determine the education caseload per community. 


### Nutrition 

Everything comes from the data sheet 
You got to look at formulas (measures) inside the pivot

Basically, I don't understand how to calculate the max by admin4pcode for nutrition: those numbers don't tally. 

Total reached: =[Total CU5]+[Total PLWs]+[MNT Adolescents]
Cumulative under 5 is the max of all under fives at the community level 
Total PLWs in the max of all PLWs at the community level 
MNT adolescents is the number of grils who received micronutrients

Max PLWs is the max of micronutrient PLWs, HEB PLWs, MAM PLWs, IYCF counselling PLWs, IYCF messaging, Mothers' support groups and FMA; however, when checking the totals, inside the sheet `Data` in the Nutrition submissions, many more activities have been included. 

Max U5 is the sum of max girls and max boys at admin4,
The specific activities included in the calculation of either max girls or boys are LNS, U5 MNP, U5 HEB, U5 Vitamin A, U5 in-patient SAM, U5 out-patient, deworming and MAM

However, much like the calculations for PLWs, when reviewing which data actually comprises the columns `Total U5 boys` and `Total U5 girls`, we note that the range of activities included is much broader than specified 

```{r}
nut %>% 
  filter(str_detect(activity, "boys|LNS")) %>%
  filter(activity %out% c("# of boys and girls (6  59 months) screened for malnutrition")) %>% 
  group_by(admin4pcode) %>% 
  slice(which.max(female)) %>% 
  select(-male) %>% 
  rename(u_ben = female) %>% 
  mutate(u_ben_type = "girls") %>% 
  rbind(nut %>% 
          filter(str_detect(activity, "boys|LNS")) %>% 
          filter(activity %out% c("# of boys and girls (6  59 months) screened for malnutrition")) %>% 
          group_by(admin4pcode) %>%
          slice(which.max(male)) %>% 
          select(-female) %>%
          rename(u_ben = male) %>%
          mutate(u_ben_type = "boys")) %>% 
  {sum(.$u_ben)}

glimpse(nut)

nut %>% count(admin4pcode)
```

Nutrition still does not tally

```{r}

nut %>% 
  filter(str_detect(activity, "PLW|IYCF|MUAC|lactating")) %>%
  filter(activity %out% c("# of health and nutrition staff trained in IYCF-E", 
                          "# of RRTs established and supported to provide CMAM and IYCF services.", 
                          "# PLWs screened for malnutrition"
                          )) %>% 
  count(activity)
  select(-male) %>% 
  rename(u_ben = female) %>% 
  mutate(u_ben_type = "PLW") %>% 
  group_by(health_facility_name, admin4pcode) %>% 
  slice(which.max(u_ben)) %>% 
  
  filter(admin3pcode == "SY020300") %>% 
  {sum(.$u_ben)}

# no maximum per community
nut %>% 
  filter(str_detect(activity, "adolescent")) %>% 
  {sum(.$female)}

SY0203000

format(662942 * 6 * 150 / 5, big.mark = ",")

glimpse(nut)
    
```

<br> 

Nutrition's 4W dataset is largely interoperable with CWG's, having all relevant cash reporting columns. The only column missing is `delivery modality`, which can largely be determined from activity descriptions and units of measurement used. To introduce a new column, assigning each row to either `cash`, `in-kind` or `service delivery` is definitely possible and does not require the template to be altered as it can be done as part of the data cleaning process, though it would be preferable for the Cluster to make that amendment themselves. 

<br><br><br>

### Protection 

#### Child protection 

-HRP indicators 5.1.1 and 5.1.2, sum of both
-Filter by the column `analaysis unit` == "People"
-Calculation uses the column `Total Reached`
-Cumulative: sum of all months

CP interventions 
-sum of the column `total cumulative interventions`, filter in all HRP indicators except 1.3.1 and "none"
-And the analysis_unit should be people 

### GBV 
-They use activity codes, and only `GBV100`, filter out `none` under the HRP indicator column 
-Calculation uses the column `new total reached`
-Filter by the column `analysis_unit` == "Beneficiaries"

GBV interventions
-sum of the column `total cumulative intervention`, for code_activity GBV200, GBV300, GBV500, GBV600, regardless of indicator or analysis unit

### Mine Action 
-Total of all activities under the sub-cluster
- sum of the column `Total reached`
-Filter by the column `analaysis unit` == "People"

MIne Action interventions 
-sum of the column `total cumulative interventions`, filter in all HRP indicators except 1.3.1 and "none"
-And the analysis_unit should be people 


### General protection 
-People reached (data and calculation pending)

General protection interventions 
-sum of the column `total cumulative interventions`, filter in all HRP indicators except 1.3.1 and "none"
-And the analysis_unit should be people 


#### Total protection

-beneficiaries is the sum of beneficiaries in child protection, mine action, GBV and general protection 


```{r}

glimpse(prot)

```

```{r}
prot %>% 
  filter(activity == "Cash assistance - GP7") %>% 
  summarise(beneficiaries = sum(total_achieved_as_per_the_unit_in_the_previous_field, na.rm = TRUE))

prot %>% count(delivery_modality)
```


Protection is only very partially interoperable with the CWG 4Ws. They do ask for `delivery modality` but transfer values, conditionality and transfer frequency are unknown. 


